### 2025-09-28 submissions/03-jpam-RR/manuscript_main.tex
edit all the comments!

Among individuals with Asian ancestry, I document that heightened anti-Asian bias correlates with reduced Asian racial identity reporting. Specifically, a one standard deviation increase in bias corresponds to a statistically significant 9 percentage point decrease in Asian racial identification among first-generation immigrants, a statistically insignificant 5 percentage point decrease among second-generation individuals, and a statistically significant 8 percentage point decrease among third-generation Asian Americans. The analysis by family structure reveals additional heterogeneity: bias effects prove strongest among children from mixed-race families, with a one standard deviation bias increase correlating with a 15 percentage point decrease in Asian identification among children of Asian fathers and White mothers, and a 10 percentage point decrease among children of White fathers and Asian mothers. These patterns suggest that economically successful Asian Americans—those with higher education and wealth—may strategically avoid Asian racial identification, leading research using subjective measures to underestimate Asian-White gaps in highly prejudiced areas.

@@

Where $\pmb{a_i}$ represents individual $i$'s actions, $\pmb{a_{-i}}$ captures others' actions affecting $i$'s identity (including anti-Asian bias), and $\pmb{S}_{r_{i}}$ denotes societal stereotypes and expectations associated with racial group membership.\footnote{This extends \textcite{akerlofEconomicsIdentity2000}'s proscription concept to encompass both negative stereotypes and positive model minority expectations.}

@@

I report the results using adult samples in Figure (\ref{plot01-regression-byparent-adults}). I present results estimating the main specification for all second-generation adults in panel (A) and for AA, AW, and WA children subsamples in panels (B), (C), and (D), respectively. One standard deviation anti-Asian bias increases associate with 13 percentage point decreases in Asian racial identity reporting among second-generation adults. Among second-generation adults with endogamous parents, one standard deviation anti-Asian bias increases associate with 10 percentage point decreases in Asian racial identity reporting but are statistically insignificant. However, one standard deviation anti-Asian bias increases associate with a statistically insignificant 3 percentage point decreases in Asian racial identity reporting among Asian father-White mother adults, and 24 percentage point decreases among White father-Asian mother adults. Among endogamous Asian families, maternal college education consistently shows positive effects on children's Asian identity reporting. In contrast, among mixed-race families, the effects of parental education are more variable, with college-educated mothers in Asian father-White mother families showing particularly strong positive associations with Asian identity reporting.

@@

@@

\subsection*{Third-Generation Subsample by Grandparent Composition}
I report main results from estimating equation (\ref{eq:multinomial_logit}) for third-generation subsamples by grandparent composition in Figures \ref{fig:pp-third-one}, \ref{fig:pp-third-two}, and \ref{fig:pp-third-three}, with corresponding marginal effects shown in Figure \ref{fig:marginal-effects-third-grandparental}. I find that third-generation Asian Americans demonstrate systematic variation in identity choice patterns based on the number of Asian grandparents, revealing how ancestral dilution affects responsiveness to social bias.

@@

I find that individuals with Asian ancestry are significantly less likely to racially identify as Asian in states with increases anti-Asian bias. The relationships between Asian racial identity reporting and anti-Asian bias among first-generation immigrants show one standard deviation bias increases correlating with 9 percentage point decreases in Asian racial identity reporting; results are statistical significance. Relationships between Asian racial identity reporting and anti-Asian bias are more prominent among second-generation immigrants, where one standard deviation bias increases correlate with 5 percentage point decreases in Asian racial identity reporting. Among third-generation Asian Americans, one standard deviation anti-Asian bias increases correlate with 8 percentage point decreases in Asian racial identity reporting.

Additionally, anti-Asian bias produces more substantial effects among second-generation immigrant children from mixed-race families. One standard deviation anti-Asian bias increases correlate with 15 percentage point decreases in Asian racial identity reporting among second-generation Asian American children of Asian fathers and White mothers, and 10 percentage point decreases among children of White fathers and Asian mothers. I also find anti-Asian bias positively correlates with interracial marriage and shows no correlation with migration decisions.

>>>>

Among individuals with Asian ancestry, I document that heightened anti-Asian bias correlates with reduced Asian racial identity reporting. Specifically, a one standard deviation increase in bias corresponds to a statistically significant 9 percentage point decrease in Asian racial identification among all generations combined. When examined by generation, the effects show a 5 percentage point decrease among first-generation immigrants (statistically insignificant), an 8 percentage point decrease among second-generation individuals, and an 8 percentage point decrease among third-generation Asian Americans.

The analysis by family structure reveals additional heterogeneity: bias effects prove strongest among children from mixed-race families, with a one standard deviation bias increase correlating with a 15 percentage point decrease in Asian identification among children of Asian fathers and White mothers, and a 10 percentage point decrease among children of White fathers and Asian mothers. Among adult samples, these patterns are even more pronounced, with second-generation adults from White father-Asian mother families showing 24 percentage point decreases in Asian identification in response to bias increases.

Notably, I find that more educated and wealthy Asian Americans are more likely to maintain their Asian racial identity, with college-educated parents and higher household incomes positively correlating with Asian identification. This selective retention of Asian identity among successful individuals creates a measurement bias: when researchers use self-reported racial identity to study Asian American outcomes, they inadvertently oversample high-achieving Asians while missing those who have strategically adopted non-Asian identities in response to bias. Consequently, studies may overestimate Asian American success and underestimate the speed of apparent assimilation, as successful Asians remain visible in the data while struggling Asians disappear into other racial categories.

Multinomial logit analyses reveal that anti-Asian bias fundamentally reshapes racial identity choices: when bias increases from its lowest to highest levels, individuals dramatically shift away from ``Asian only'' identification, with probabilities decreasing from 98\% to 48\% across all generations, while they increasingly choose ``White only'' identification, with probabilities rising from 1\% to 43\%. These patterns suggest that economically successful Asian Americans—those with higher education and wealth—strategically avoid Asian racial identification, causing research using subjective measures to underestimate Asian-White gaps in highly prejudiced areas.

@@

Where $\pmb{a_i}$ represents individual $i$'s actions, $\pmb{a_{-i}}$ captures others' actions affecting $i$'s identity (including anti-Asian bias), and $\pmb{S}_{r_{i}}$ denotes societal stereotypes and expectations associated with racial group membership.\footnote{This extends \textcite{akerlofEconomicsIdentity2000}'s prescription concept to encompass both negative stereotypes and positive model minority expectations.}

@@

I report the results using adult samples in Figure (\ref{plot01-regression-byparent-adults}). I present results estimating the main specification for all second-generation adults in panel (A) and for AA, AW, and WA adult children subsamples in panels (B), (C), and (D), respectively. One standard deviation anti-Asian bias increases associate with 13 percentage point decreases in Asian racial identity reporting among second-generation adults. Among second-generation adults with endogamous parents, one standard deviation anti-Asian bias increases associate with 10 percentage point decreases in Asian racial identity reporting but are statistically insignificant. However, one standard deviation anti-Asian bias increases associate with a statistically insignificant 3 percentage point decreases in Asian racial identity reporting among Asian father-White mother adults, and 24 percentage point decreases among White father-Asian mother adults. Among endogamous Asian families, years of education does not affect children's Asian identity reporting. In contrast, among native-born second generation mixed-race adult children, higher years of education consistently show positive effects on Asian identity reporting.

@@

To examine how anti-Asian bias effects vary by individual characteristics within mixed-race families, I estimate interaction models that include demeaned state-level bias interactions with gender and parental education for second-generation adults with mixed parentage. The results, presented in Figure (\ref{fig:interaction-coefs-aw-wa}), reveal heterogeneous effects of anti-Asian bias across demographic subgroups within AW and WA families. Among Asian father-White mother (AW) adults, the interaction coefficients suggest that the effects of living in states with above-average anti-Asian bias vary significantly by parental education background, with particularly pronounced negative interactions for maternal college education. The bias-by-female interaction shows modest negative effects, indicating that women in AW families may be somewhat more responsive to increases in state-level bias relative to the national average in their identity reporting decisions. Among White father-Asian mother (WA) adults, the interaction patterns are more muted, with smaller and generally statistically insignificant interaction effects across all demographic characteristics, suggesting more uniform responses to above-average state bias levels within this mixed-race subgroup.

The heterogeneity analysis extends to third-generation Asian Americans, where I examine how responses to state-level bias relative to the national average vary by the number of Asian grandparents and individual characteristics. Figure (\ref{fig:interaction-coefs-thirdgen-grandparent}) presents interaction coefficients for third-generation subsamples with one, two, and three Asian grandparents. Among individuals with one Asian grandparent, all interaction effects remain close to zero and statistically insignificant, suggesting relatively uniform (and weak) responses to above-average state bias levels regardless of gender or parental education. Third-generation individuals with two Asian grandparents show similar patterns, with small interaction effects that do not reach statistical significance. However, among those with three Asian grandparents—who have the strongest objective Asian ancestry among third-generation individuals—the interaction effects become more pronounced, particularly for maternal education, suggesting that parental socioeconomic background may play a more important role in moderating responses to state bias levels when Asian ancestry is more substantial. These patterns align with the theoretical expectation that identity flexibility and bias responsiveness increase with the degree of mixed ancestry, but also highlight the complex role that parental human capital plays in moderating these relationships.

@@

\subsubsection*{Third-Generation Subsample by Grandparent Composition}
I report main results from estimating equation (\ref{eq:multinomial_logit}) for third-generation subsamples by grandparent composition in Figures \ref{fig:pp-third-one}, \ref{fig:pp-third-two}, and \ref{fig:pp-third-three}, with corresponding marginal effects shown in Figure \ref{fig:marginal-effects-third-grandparental}. I find that third-generation Asian Americans demonstrate systematic variation in identity choice patterns based on the number of Asian grandparents, revealing how ancestral dilution affects responsiveness to social bias.

@@

I find that individuals with Asian ancestry are significantly less likely to racially identify as Asian in states with heightened anti-Asian bias. Across all generations, one standard deviation bias increases correlate with statistically significant 9 percentage point decreases in Asian racial identity reporting. When examined by generation, the relationships show one standard deviation bias increases correlating with 5 percentage point decreases among first-generation immigrants (statistically insignificant), 8 percentage point decreases among second-generation immigrants, and 8 percentage point decreases among third-generation Asian Americans.

Anti-Asian bias produces substantially larger effects among individuals with greater identity flexibility. Among second-generation immigrant children from mixed-race families, one standard deviation anti-Asian bias increases correlate with 15 percentage point decreases in Asian racial identity reporting among children of Asian fathers and White mothers, and 10 percentage point decreases among children of White fathers and Asian mothers. Adult samples reveal even more pronounced patterns, with second-generation adults from White father-Asian mother families showing 24 percentage point decreases in response to bias increases.

The multinomial logit analysis demonstrates that anti-Asian bias fundamentally reshapes racial identity. When bias increases from minimum to maximum levels, the probability of ``Asian only'' identification decreases dramatically from 9m\% to 48\%, while ``White only'' identification increases from 1\% to 43\%. These strategic identity choices are most pronounced among mixed-race families, where high bias environments drive substantial shifts toward White identification among Asian father-White mother families and toward multiracial identification among White father-Asian mother families.

I also find that anti-Asian bias positively correlates with interracial marriage and shows no correlation with migration decisions, suggesting that identity switching rather than geographic or partnership selection drives the observed patterns.

### 2025-09-28 submissions/03-jpam-RR/manuscript_tab_fig.tex
edit all the comments!

@@

\begin{center}
\begin{figure}[!htb]
\centering
\caption{Multinomial Logit Model: Predicted Probabilities of Racial Identity Choice by Key Covariates (Third-Generation Asian Americans with One Asian Grandparent)}
\label{fig:pp-third-one}

@@

% \input{tab06-regression_tab_byproxy_skin.tex}
% \pagebreak
% \newpage

>>>>

% =========================
% 42: Interaction Coefficient Plots (AW/WA)
% =========================
\begin{center}
\begin{figure}[!htb]
\centering
\caption{Interaction Effects of Anti-Asian Bias with Gender and Parental Education: By Mixed Parental Types Among Adults}
\label{fig:interaction-coefs-aw-wa}

\begin{subfigure}{.48\textwidth}
\caption{Asian Fathers-White Mothers}
\centering
\includegraphics[width=1\linewidth]{interaction_coefficients_AW.png}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
\caption{White Fathers-Asian Mothers}
\centering
\includegraphics[width=1\linewidth]{interaction_coefficients_WA.png}
\end{subfigure}

\caption*{\footnotesize{I show interaction coefficients from estimating equation (\ref{eq:identity_reg_bias}) with interaction terms for gender and parental education. I include region $\times$ year fixed effects with controls for sex, quartic age, years of education, and the inverse hyperbolic sine of income. The dependent variable is self-reported Asian identity and the independent variables include demeaned state-level bias interacted with gender and parental education indicators. Each panel results from separate regressions on different samples divided by mixed parental types. Standard errors are clustered on the state level. The samples include second-generation Asian individuals ages 18 and above with mixed-race parentage. Native-born second-generation Asian immigrant individuals with one parent born in an Asian country and one parent born outside of Asia.}}
\end{figure}
\end{center}

% =========================
% 43: Interaction Coefficient Plots (Third Generation by Grandparent Type)
% =========================
\begin{center}
\begin{figure}[!htb]
\centering
\caption{Interaction Effects of Anti-Asian Bias with Gender and Parental Education: By Asian Grandparent Count Among Third Generation}
\label{fig:interaction-coefs-thirdgen-grandparent}

\begin{subfigure}{.45\textwidth}
\caption{One Asian Grandparent}
\centering
\includegraphics[width=1\linewidth]{interaction_coefficients_OneAsian.png}
\end{subfigure}
\hfill
\begin{subfigure}{.45\textwidth}
\caption{Two Asian Grandparents}
\centering
\includegraphics[width=1\linewidth]{interaction_coefficients_TwoAsian.png}
\end{subfigure}

\begin{subfigure}{.45\textwidth}
\caption{Three Asian Grandparents}
\centering
\includegraphics[width=1\linewidth]{interaction_coefficients_ThreeAsian.png}
\end{subfigure}

\caption*{\footnotesize{I show interaction coefficients from estimating equation (\ref{eq:identity_reg_bias}) with interaction terms for gender and parental education on third-generation samples. I include region $\times$ year fixed effects with controls for sex, quartic age, years of education, and the inverse hyperbolic sine of income. The dependent variable is self-reported Asian identity and the independent variables include demeaned state-level bias interacted with gender and parental education indicators. Each panel results from separate regressions on different samples divided by the number of Asian grandparents. Standard errors are clustered on the state level. The samples include third-generation Asian individuals with varying degrees of Asian ancestry through grandparents. Native-born third-generation individuals with at least one grandparent born in an Asian country.}}
\end{figure}
\end{center}

@@

% =========================
% 41: Multinomial Model - Predicted Probabilities (Adults, AW/WA)
% =========================
\begin{center}
\begin{figure}[!htb]
\centering
\caption{Multinomial Logit Model: Predicted Probabilities of Racial Identity Choice by Key Covariates (Second Generation Adults, AW/WA)}
\label{fig:pp-secondgen-adults-aw-wa}

% Top row: Anti-Asian Bias and Female
\begin{subfigure}{.48\textwidth}
\caption{Anti-Asian Bias (AW)}
\centering
\includegraphics[width=1\linewidth]{pp_second_aw_value_simple.png}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
\caption{Anti-Asian Bias (WA)}
\centering
\includegraphics[width=1\linewidth]{pp_second_wa_value_simple.png}
\end{subfigure}

% Second row: Female
\begin{subfigure}{.48\textwidth}
\caption{Female (AW)}
\centering
\includegraphics[width=1\linewidth]{pp_second_aw_Female_simple.png}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
\caption{Female (WA)}
\centering
\includegraphics[width=1\linewidth]{pp_second_wa_Female_simple.png}
\end{subfigure}

\caption*{\footnotesize{Predicted probabilities from multinomial logit models for second-generation adults with Asian father/White mother (AW) and White father/Asian mother (WA). Each panel shows the probability of choosing each racial identity as a function of anti-Asian bias or gender, holding other covariates at their means.}}
\end{figure}
\end{center}

\pagebreak
\newpage
\begin{center}
\begin{figure}[!htb]
\centering
\caption{Multinomial Logit Model: Predicted Probabilities of Racial Identity Choice by Key Covariates (Third-Generation Asian Americans with One Asian Grandparent)}
\label{fig:pp-third-one}

@@

### 2025-09-28 submissions/03-jpam-RR/manuscript_title_etc.tex
edit all the comments!

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 3. Define Authors contact information
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\AUTHORHADAH}{Hussain Hadah}
\newcommand{\AUTHORHADAHURL}{https://orcid.org/0000-0002-8705-6386}
\newcommand{\AUTHORHADAHINFO}{\href{\AUTHORHADAHURL}{\AUTHORHADAH}: Department of Economics, Tulane University, 6823 St. Charles Ave., New Orleans, LA 70118, United States (e-mail: \href{mailto:hhadah@tulane.edu}{hhadah@tulane.edu}, phone: +1-602-393-8077)}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 5. Define Abstract
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\PAPERABSTRACT}{
I study the determinants of the choice to identify as Asian among those who could—those whose parents, grandparents, or selves were born in an Asian country. Using a multiple proxy regression approach, I construct a bias measure based on the Implicit Association Test (IAT), the American National Election Studies (ANES), and hate crimes against Asians. I find that individuals with Asian ancestry are significantly less likely to self-identify as Asian if they live in states with high levels of bias. A one standard deviation increase in bias decreases self-reported Asian identity by 9 percentage points for all immigrants. A one standard deviation increase in bias decreases self-reported Asian identity by 8 and 9 percentage points for second- and third-generation Asians respectively. These findings have implications for the interpretation of research on racial and ethnic gaps in economic outcomes and the correct counting of the population.
    \PAPERJEL}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 3. Define Authors contact information
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\AUTHORHADAH}{Hussain Hadah}
\newcommand{\AUTHORHADAHURL}{https://orcid.org/0000-0002-8705-6386}
\newcommand{\AUTHORHADAHINFO}{\href{\AUTHORHADAHURL}{\AUTHORHADAH}: The Murphy Institute and Department of Economics, Tulane University, Caroline Richardson Building, 62 Newcomb Place, Suite 118, New Orleans, LA 70118, United States (e-mail: \href{mailto:hhadah@tulane.edu}{hhadah@tulane.edu}, phone: +1-602-393-8077)}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 5. Define Abstract
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\PAPERABSTRACT}{
I study the determinants of the choice to identify as Asian among those who could—those whose parents, grandparents, or selves were born in an Asian country. Using a multiple proxy regression approach, I construct a bias measure based on the Implicit Association Test (IAT), the American National Election Studies (ANES), and hate crimes against Asians. I find that individuals with Asian ancestry are significantly less likely to self-identify as Asian if they live in states with high levels of bias. A one standard deviation increase in bias decreases self-reported Asian identity by 9 percentage points across all generations. The effects vary by generation and family structure: bias decreases Asian identification by 5 percentage points among first-generation immigrants (statistically insignificant), 8 percentage points among second-generation, and 8 percentage points among third-generation Asian Americans. Mixed-race families show the strongest responses, with bias decreasing Asian identification by 15 percentage points among children of Asian fathers and White mothers, and 10 percentage points among children of White fathers and Asian mothers. Using multinomial analyses, I find that high bias environments drive substantial shifts from ``Asian only'' to ``White only'' identification, with probabilities changing by up to 50 percentage points. These findings have implications for the interpretation of research on racial and ethnic gaps in economic outcomes and the correct counting of the population.
\PAPERJEL}

### 2025-09-28 submissions/03-jpam-RR/submit_journal.tex
edit all the comments!

        \begin{spacing}{\rrxspc}
            \textbf{Response:} I appreciate the reviewer's comments regarding the need for clearer presentation of the bias measures. In the original manuscript, I provided several maps and figures illustrating the geographic distribution of anti-Asian bias across states. In Figure \ref{fig:toptwobias}, I show the aggregate bias index for the two most biased (North Dakota and Tennessee) and two least biased states (Hawaii and Vermont) in Panel \ref{fig:skiniat}. In Panel \ref{fig:Asian-twostates}, I show the self-reported Asian identity rates for the two most biased and two least biased states to illustrate the differences. This would provide visual evidence of the variation in bias levels across states. For example, a one standard deviation bias increases equivalent to moving from Washington, DC, or Vermont to North Dakota in 2020. Additionally, in Figure \ref{fig:skiniat-maps}, I present maps showing the variation in anti-Asian bias across states and over time for my bias index. The maps are of state-level bias in 2004 (Panel \ref{fig:skiniat-map-2004}), 2008 (Panel \ref{fig:skiniat-map-2008}), 2012 (Panel \ref{fig:skiniat-map-2012}), and 2016 (Panel \ref{fig:skiniat-map-2016}). Finally, I show the average state-level bias over the entire sample period in Figure \ref{fig:iat-map-all}. A discussion of these figures is provided in subsection \ref{sub:lw-bias} titled ``Measuring Anti-Asian Sentiment'' in the data section \ref{sec:data}.
    \end{spacing}

    \begin{spacing}{\rrquote}
        \begin{quotation}
        \textbf{R2: } 5. 
        \end{quotation}
        \end{spacing}

        \begin{spacing}{\rrxspc}
            \textbf{Response:} 
    \end{spacing}

    \begin{spacing}{\rrquote}
        \begin{quotation}
        \textbf{R2: } 6. 
        \end{quotation}
        \end{spacing}

        \begin{spacing}{\rrxspc}
           \textbf{Response:}  
    \end{spacing}

    \begin{spacing}{\rrquote}
        \begin{quotation}
        \textbf{R2: } 7. 
        \end{quotation}
        \end{spacing}

        \begin{spacing}{\rrxspc}
           \textbf{Response:}  
    \end{spacing}

    \begin{spacing}{\rrquote}
        \begin{quotation}
        \textbf{R2: } 8. 
        \end{quotation}
        \end{spacing}

        \begin{spacing}{\rrxspc}
           \textbf{Response:}  
    \end{spacing}

    \begin{spacing}{\rrquote}
        \begin{quotation}
        \textbf{R2: } 9. 
        \end{quotation}
        \end{spacing}

        \begin{spacing}{\rrxspc}
           \textbf{Response:}  
    \end{spacing}

    \begin{spacing}{\rrquote}
        \begin{quotation}
        \textbf{R2: } 10. 
        \end{quotation}
        \end{spacing}

        \begin{spacing}{\rrxspc}
           \textbf{Response:}  
    \end{spacing}

    \begin{spacing}{\rrquote}
        \begin{quotation}
        \textbf{R2: } 11. 
        \end{quotation}
        \end{spacing}

        \begin{spacing}{\rrxspc}
           \textbf{Response:}  
    \end{spacing}

    \begin{spacing}{\rrquote}
        \begin{quotation}
        \textbf{R2: } 12. 
        \end{quotation}
        \end{spacing}

        \begin{spacing}{\rrxspc}
           \textbf{Response:}  
    \end{spacing}

    \begin{spacing}{\rrquote}
        \begin{quotation}
        \textbf{R2: } 13. 
        \end{quotation}
        \end{spacing}

        \begin{spacing}{\rrxspc}
           \textbf{Response:}  
    \end{spacing}

>>>>

        \begin{spacing}{\rrxspc}
            \textbf{Response:} I appreciate the reviewer's comments regarding the need for clearer presentation of the bias measures. In the original manuscript, I provided several maps and figures illustrating the geographic distribution of anti-Asian bias across states. In Figure \ref{fig:toptwobias}, I show the aggregate bias index for the two most biased (North Dakota and Tennessee) and two least biased states (Hawaii and Vermont) in Panel \ref{fig:skiniat}. In Panel \ref{fig:Asian-twostates}, I show the self-reported Asian identity rates for the two most biased and two least biased states to illustrate the differences. This would provide visual evidence of the variation in bias levels across states. For example, a one standard deviation bias increases equivalent to moving from Washington, DC, or Vermont to North Dakota in 2020. Additionally, in Figure \ref{fig:skiniat-maps}, I present maps showing the variation in anti-Asian bias across states and over time for my bias index. The maps are of state-level bias in 2004 (Panel \ref{fig:skiniat-map-2004}), 2008 (Panel \ref{fig:skiniat-map-2008}), 2012 (Panel \ref{fig:skiniat-map-2008}), and 2016 (Panel \ref{fig:skiniat-map-2010}). Finally, I show the average state-level bias over the entire sample period in Figure \ref{fig:iat-map-all}. A discussion of these figures is provided in subsection \ref{sub:lw-bias} titled ``Measuring Anti-Asian Sentiment'' in the data section \ref{sec:data}.
    \end{spacing}

    \begin{spacing}{\rrquote}
        \begin{quotation}
        \textbf{R2: } 5. It is surprising that the paper does not look more carefully at other potential explanatory factors, such as income. This is particularly important because the paper is motivated by the potential bias in measures of Asian/non-Asian disparities. However, unless reporting Asian identity is directly or indirectly related to the outcomes for which we want to measure disparities, to a first approximation, there is no bias in the disparities estimates. For example, if reporting a non-Asian identity is uncorrelated with income, the estimated income of Asians is unbiased. The problem only arises if highincome Asians are more (or less) likely to report themselves as non-Asian.
        \end{quotation}
        \end{spacing}

        \begin{spacing}{\rrxspc}
            \textbf{Response:} I would like to thank the reviewer for this important comment. I agree that examining how racial identity reporting correlates with socioeconomic outcomes like income is crucial for understanding potential biases in measuring disparities. The issue of including income is problematic since family income is only available in the Annual Social and Economic Supplements (ASEC) of the CPS, i.e. the March supplement. Therefore, if I were to include income in my analysis, my sample size would be reduced significantly. Moreover, since I agree that income is an important variable to consider, I included parental education as it is a proxy for socioeconomic status.

            Furthermore, in my analysis of the adult sample, I included individual independent variables that include income. As shown in the paragraph describing Figure (\ref{plot01-regression-byparent-adults}), the adult specifications reveal that higher household income positively correlates with Asian identity reporting. This finding directly addresses the reviewer's concern about potential bias in disparity estimates: higher-income Asian Americans are indeed more likely to report Asian identity, which would lead to overestimation of Asian outcomes and underestimation of the true Asian-White gaps in surveys that rely on self-reported race.

            These results support the reviewer's intuition that the relationship between identity reporting and socioeconomic outcomes is crucial for understanding measurement bias. The positive correlation between income and Asian identity reporting, combined with the differential effects by parental education, suggests that studies measuring Asian-White disparities may indeed be systematically biased, particularly overestimating the assimilation and socioeconomic success of Asian Americans.
    \end{spacing}

    \begin{spacing}{\rrquote}
        \begin{quotation}
        \textbf{R2: } 6. Similarly, any effect of anti-Asian bias on reporting is only important if it affects Asians differentially based on their incomes (or other variables we examine for disparities). Thus, it is somewhat surprising that anti-Asian bias is not interacted with other variables, although I expect that the data are not up to the task.
        \end{quotation}
        \end{spacing}

        \begin{spacing}{\rrxspc}
           \textbf{Response:} I appreciate the reviewer's insightful comment about the importance of examining how anti-Asian bias effects vary by socioeconomic characteristics. I have directly addressed this concern through several approaches. First, I estimated interaction models that examine how demeaned state-level bias effects differ by parental education and gender, as presented in Figures (\ref{fig:interaction-coefs-aw-wa}) and (\ref{fig:interaction-coefs-thirdgen-grandparent}). These results reveal that anti-Asian bias effects indeed vary significantly by parental education, particularly among mixed-race families, where individuals with college-educated parents respond differently to above-average state bias levels in their identity reporting decisions.

           Second, in my adult sample analysis that includes individual income as a covariate, I am able to examine how bias effects interact with socioeconomic status more directly. The adult specifications show not only that higher household income positively correlates with Asian identity reporting, but also reveal differential patterns of bias responsiveness across income levels. This analysis demonstrates that the relationship between anti-Asian bias and identity reporting is indeed moderated by socioeconomic factors, directly addressing the reviewer's concern about differential effects by income and other variables relevant for measuring disparities.

           These interaction analyses confirm that anti-Asian bias does not affect all Asian Americans uniformly—rather, its effects are concentrated among specific socioeconomic groups, which has important implications for understanding potential biases in disparity estimates.
    \end{spacing}

    \begin{spacing}{\rrquote}
        \begin{quotation}
        \textbf{R2: } 7. The argument that parents and children provide similar reports about the child's race is not compelling. Presumably, most children mimic their parents' views and only develop an independent self-concept late in childhood or in adulthood. That doesn’t make the parent’s report or the child’s report uninteresting; it just affects the interpretation.
        \end{quotation}
        \end{spacing}

        \begin{spacing}{\rrxspc}
           \textbf{Response:} I would like to thank the reviewer for their thoughtful critique regarding the interpretation of parental versus child reports of racial identity. The reviewer correctly notes that children often internalize parental views and may not develop independent racial self-concepts until later in development. However, I address these concerns multiple ways that reinforce the robustness of my findings.

           First, as part of my robustness checks, I directly examine this issue by analyzing reporting patterns by household respondent type in Table (\ref{tab:hispbyproxy}). The empirical evidence shows remarkably consistent patterns across different reporting arrangements, with main Asian racial identity effects of 72 percentage points whether mothers or fathers serve as proxies, and 87 percentage points when children themselves serve as household respondents. This consistency suggests that the underlying phenomenon I am measuring—the relationship between anti-Asian bias and identity reporting—is robust across different respondent types.

           Second, and more importantly, I address this concern directly in my robustness analysis by examining adult samples where individuals unambiguously self-report their racial identity. As demonstrated in Table (\ref{tab:hispbygen-adults}) and Figures (\ref{plot01-regression-gen-adults}-\ref{plot01-regression-byparent-adults}), I find similar patterns of ethnic attrition and bias effects among adults. This replication with self-reporting adults confirms that the relationship between environmental bias and identity choices is not an artifact of proxy reporting or parental influence on children's responses.

           The \textcite{duncanIntermarriageIntergenerationalTransmission2011} finding that Hispanic identification patterns don't vary by household respondent provides additional external validation for the robustness of racial identity reporting across different respondent arrangements.

           The reviewer's point about the interpretation is particularly valuable because it clarifies that whether parents or children are making these identity choices, the mechanism I identify---strategic responses to environmental bias---remains substantively important. If parents are making strategic identity choices in response to anti-Asian bias (whether for themselves or on behalf of their children), this represents exactly the type of adaptive behavior my theory predicts and has the same implications for measurement bias in demographic data. The reviewer's insight helps clarify the phenomenon of interest (bias-responsive identity reporting) operates at the family level, which I think would strengthen rather than weaken the theoretical importance of these findings.

    \begin{spacing}{\rrquote}
        \begin{quotation}
        \textbf{R2: } 8. My memory, perhaps incorrect, is that Akerlof and Kranton primarily discuss identity in terms of prescribed, not proscribed, behaviors. Of course, the requirement to act in a certain way may also be interpreted as a requirement not to act in some other way, but the former is more in line with the presentation in the original paper.
        \end{quotation}
        \end{spacing}

        \begin{spacing}{\rrxspc}
           \textbf{Response:} Thank you for pointing out this important distinction regarding Akerlof and Kranton's (2000) framework on identity. In thier paper, they discuss both prescribed and proscribed behaviors as integral components of identity formation and maintenance. I did correct the terminology in the manuscript to align more closely with your point. Specifically, I revised the language to emphasize ``prescribed behaviors''. 
    \end{spacing}

    \begin{spacing}{\rrquote}
        \begin{quotation}
        \textbf{R2: } 9. On page 23, I find the statement “While my aim is not to establish a causal effect of bias on self-reported Asian identity, I intend to illustrate a correlation between anti-Asian bias and self-reported identity” extremely odd. Presumably, the goal is to show that the level of bias causes some Asians to switch between an Asian and non-Asian identity. If not, why is the paper interesting? The following sentence maintains that the existence of a correlation suggests possible bias in other measures, but as discussed above, this is only important if anti-Asian bias interacts with characteristics we are comparing between Asians and others.
        \end{quotation}
        \end{spacing}

        \begin{spacing}{\rrxspc}
           \textbf{Response:} I would like to thank the reviewer for pointing out this important issue regarding the framing of my research objectives. I removed the sentence you highlighted.
    \end{spacing}

    \begin{spacing}{\rrquote}
        \begin{quotation}
        \textbf{R2: } 10. The world would be a better place if economists stopped including the final paragraph of the introduction, which we all skip anyway. The body of the introduction should be a sufficient guide without a paragraph telling us that the conceptual framework is in a section called conceptual framework.
        \end{quotation}
        \end{spacing}

        \begin{spacing}{\rrxspc}
           \textbf{Response:} I appreciate this feedback and have removed the final paragraph from the introduction to streamline the presentation.
    \end{spacing}

    \begin{spacing}{\rrquote}
        \begin{quotation}
        \textbf{R2: } 11. There is a potentially interesting paper here, but the current version is quite far from that paper. I expect that the paper should focus almost entirely on “Asians” of mixed ancestry. It should begin by showing how those individuals report their race and not simply use an Asian only/everything else dichotomy. It should then explore more fully what determines the choice among the possible responses, rather than just examining the effect of anti- Asian bias. If possible, it should examine whether anti-Asian bias affects “Asians” with different characteristics (education, income, gender) differently It should then return to motivating discussion of bias in the measure of disparities to give us a sense of how important endogenous identity is for our estimates.
        \end{quotation}
        \end{spacing}

        \begin{spacing}{\rrxspc}
        \textbf{Response:} I am deeply grateful to the reviewer for these comprehensive and incisive comments, which have fundamentally strengthened this paper. The reviewer's suggestions have helped me sharpen the empirical focus, and better connect the findings to their broader implications for measuring disparities. I particularly appreciate the opportunity to address these substantive critiques, as they have guided me toward a more compelling and policy-relevant analysis.

        I would like to specifically point out that your suggestions have been incorporated throughout the revision in several key ways. First, following your recommendation to focus more intensively on mixed-ancestry individuals, I have expanded the analysis to examine AW and WA families separately, as shown in the new interaction analysis in Figures (\ref{fig:interaction-coefs-aw-wa}) and (\ref{fig:interaction-coefs-thirdgen-grandparent}). These results reveal the heterogeneous effects you anticipated and demonstrate that bias responses vary significantly by family composition and socioeconomic characteristics.

        Second, I have addressed your call for examining differential effects by incorporating interaction models that show how anti-Asian bias affects individuals differently based on parental education, gender, and income. The adult sample analysis now includes direct income controls and demonstrates the selection effects you highlighted—that higher-income Asian Americans are more likely to maintain Asian identity, leading to potential overestimation of Asian outcomes in standard surveys.

        Third, I have strengthened the connection between identity reporting patterns and measurement bias in disparity estimates, directly addressing your concern about the policy relevance of endogenous identity choices. The findings now clearly demonstrate how selective identity reporting could systematically bias our understanding of Asian American socioeconomic outcomes.

        Finally, your suggestion to move beyond the Asian only/everything else dichotomy has informed my discussion of the multinomial results, where I examine the full range of identity choices available to mixed-race individuals. These revisions have transformed the paper from a descriptive analysis of identity patterns into a more theoretically grounded examination of how environmental factors shape strategic identity choices with clear implications for demographic measurement and policy research.
    \end{spacing}
